Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-11-02 VMCAI-revised-version/final.tex
up

 \begin{center}
 	\begin{figure}
 	\hspace{-2.cm}
\includegraphics[width=1.40\textwidth]{All_results}
\caption{Hasse diagram of some classes of transition systems, together with the decidability (in green) or undecidability (in red) of the resilience problems. Decidability of bounded resilience and $k-$resilience variants are indicated in blue.}
	\end{figure}
\end{center}

@@

% 
\fi
{\sc Resilience} (and {\sc $t$-liveness}) needs a set (resp. a transition) to always remains reachable (resp. fireable), while
{\sc zero-reachability} concerns itself only with the existence of at least one way to reach some state $q_f(\textbf{0})$,
which could be unreachable from other reachable states. 
%
Despite this it is possible to reduce 
the {\sc zero-reachability} 
to
{\sc $t$-liveness}.
% The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets,
The following Proposition is a variation  to reset-VASS 
of~\cite[Theorem~5.5]{peterson1981petri} originally stated for Petri nets,
 whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
{\sc zero-reachability} can be reduced to {\sc $t$-liveness}.
\end{proposition}

@@

Let us recall the {\sc zero-reachability} problem in (reset-)VASS.

>>>>

 \begin{center}
 	\begin{figure}
 	\hspace{-2.cm}
\includegraphics[width=1.40\textwidth]{All_results}
\caption{Hasse diagram of some classes of transition systems, together with the decidability (in green) or undecidability (in red) of the resilience problems. Decidability of bounded resilience and $k-$resilience variants are indicated in blue.}
	\end{figure}
\end{center}
\newpage

@@

% 
\fi
\iffalse {\sc Resilience} (and {\sc $t$-liveness}) needs a set (resp. a transition) to always remains reachable (resp. fireable), while
{\sc zero-reachability} concerns itself only with the existence of at least one way to reach some state $q_f(\textbf{0})$,
which could be unreachable from other reachable states. 
%
Despite this it is possible to reduce 
 {\sc zero-reachability} 
to
{\sc $t$-liveness}.
\fi
% The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets,
The following Proposition is a variation  to reset-VASS 
of~\cite[Theorem~5.5]{peterson1981petri} originally stated for Petri nets,
 whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
{\sc zero-reachability} can be reduced to {\sc $t$-liveness}.
\end{proposition}

@@

Let us recall the {\em zero-reachability} problem in (reset-)VASS.
